A thermodynamic view of dusty protoplanetary disks

### 2017-06-29 paper.tex
added GW73 as original source (I believe, but perhaps Safronov...) of dust KHI (before Weidenschilling 1980, etc.).  Treatment was not modern (Ekman layers etc) but was the basic idea and historically important.
Minor tweaks, switching J11 for J06 as a pioneering work with two way drag forces on lagrangian particles

\section{Introduction}
%si, sgi as examples
Protoplanetary disks are comprised of a mixture of gas and dust
\citep{chiang10}. Although the overall dust content is small
($\sim 1\%$ by mass), their presence can have profound impacts on the 
gas dynamics and vice versa. Dust-gas friction introduces phenomena
that are absent in pure gas disks. Important examples include the
streaming instability 
\citep[SI,][]{youdin05a,youdin07b,johansen07}, secular gravitational
instabilities \citep[SGI,][]{ward00,youdin11,michikoshi12,takahashi14} and
Kelvin-Helmholtz instabilities
\citep{chiang08,barranco09,lee10}. These lead to structure and
planetesimal formation, as well as turbulence. 
More recently, new 
dusty instabilities have also been uncovered through numerical
simulations \citep{loren15,loren16,lamb16}, but these are not yet well
understood.

%particles 
Current state-of-the-art models of dusty protoplanetary
disks directly simulate gas dynamics coupled to explicit
Lagragian dust particles
\citep{nelson10,bai10,johansen11,yang14,zhu14,gibbons15,simon16,baruteau16}. 
The equation of motion for each particle is solved 
including dust-gas drag; the strength of which is measured 
by a stopping time $\tstop$ --- the decay timescale for the 
relative velocity between gas and dust. Thus small $\tstop$
corresponds to tightly-coupled particles.

@@

Another approach is to model the dust population as a continous, pressureless
fluid 
\citep{paardekooper06b,meheut12,laibe12,loren14,fu14b,surville16}. The 
hydrodynamic equations are evolved for two fluids: the gas and dust with density and
velocity $\rhog$, $\bm{v}_\mathrm{g}$ and $\rhod$, 
$\bm{v}_\mathrm{d}$, respectively. Source terms are introduced into
the momentum/energy equations to model dust-gas drag. This approach
can take advantage of existing numerical methods/codes for
simulating pure gas dynamics.

>>>>

\section{Introduction}
%si, sgi as examples
Protoplanetary disks are comprised of a mixture of gas and dust
\citep{chiang10}. Although the overall dust content is small
($\sim 1\%$ by mass), their presence can have profound impacts on the 
gas dynamics and vice versa. Dust-gas friction introduces phenomena
that are absent in pure gas disks. Important examples include the
streaming instability 
\citep[SI,][]{youdin05a,youdin07b,johansen07}, secular gravitational
instabilities \citep[SGI,][]{ward00,youdin11,michikoshi12,takahashi14} and
Kelvin-Helmholtz instabilities
\citep{goldreich1973, chiang08,barranco09,lee10}. These instabilities 
can trigger turbulence, and (in different regimes) promote or inhibit 
planetesimal formation. 
More recently, new 
dusty instabilities have appeared in numerical
simulations \citep{loren15,loren16,lamb16}, but their physical underpinnings are not yet well
understood.

%particles 
Current state-of-the-art models of dusty protoplanetary
disks directly simulate gas dynamics coupled to explicit
Lagragian dust particles
\citep{johansen2006, nelson10,bai10,yang14,zhu14,gibbons15,simon16,baruteau16}. 
The equation of motion for each particle is solved 
including dust-gas drag; the strength of which is measured 
by a stopping time $\tstop$ --- the decay timescale for the 
relative velocity between gas and dust. Thus small $\tstop$
corresponds to tightly-coupled particles.

@@

Another approach is to model the dust population as a continuous, pressureless
fluid 
\citep{paardekooper06b,meheut12,laibe12,loren14,fu14b,surville16}. The 
hydrodynamic equations are evolved for two fluids: the gas and dust with density and
velocity $\rhog$, $\bm{v}_\mathrm{g}$ and $\rhod$, 
$\bm{v}_\mathrm{d}$, respectively. Source terms are introduced into
the momentum/energy equations to model dust-gas drag. This approach
can take advantage of existing numerical methods/codes for
simulating pure gas dynamics.
